\documentclass[10pt,a4paper]{extarticle}
\pagenumbering{gobble}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx}
\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\begin{document}
\begin{center}
    \begin{minipage}{\textwidth}
        \centering
        {\LARGE\textbf{Ertan Şinik}} \hspace{2pt} {\LARGE{Seniro Mobile Developer}}\\[10pt]
        \href{mailto:ertansinik@gmail.com}{ertansinik@gmail.com} \textbullet\
        \href{https://linkedin.com/in/sinikertan}{linkedin.com/in/sinikertan} \textbullet\
        \href{https://github.com/esinik}{github.com/esinik}
    \end{minipage}
\end{center}
\section{Summary}
As a Senior Mobile Developer with over a decade of experience, I specialize in building innovative, high-performance mobile applications across iOS, Android, and cross-platform frameworks such as Flutter. My background combines deep technical expertise with strong leadership skills, enabling me to deliver scalable solutions while guiding teams through complex development challenges.

Throughout my career, I have successfully designed and deployed applications that blend seamless user experiences with robust architectures, integrating modern technologies such as real-time communication, offline data management, and cloud services. My approach emphasizes clean code, maintainability, and performance optimization, ensuring long-term value for both users and businesses.

Driven by curiosity and continuous learning, I stay up to date with the latest mobile technologies and best practices. I am passionate about creating products that not only solve real problems but also inspire users through intuitive design and smooth functionality.
\section{Experience}
\textbf{\href{https://inity.com.tr}{Inity}. \textit{(Istanbul, Türkiye)}} \hfill Hybrid\\
\textit{Mobile Team Lead} \hfill January 2025 -- Present
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Led the Mobile Development Team across iOS, Android, and Flutter projects.
	\item Drove architectural decisions and optimized build/release pipelines.
	\item Guided the transition to modern state management (Riverpod) and offline-first databases.
	\item Mentored developers through code reviews and best practices.
	\item Ensured seamless API integrations and real-time communication features.
\end{itemize}
\textbf{\href{https://inity.com.tr}{Inity}. \textit{(Istanbul, Türkiye)}} \hfill Hybrid\\
\textit{Senior Software Developer} \hfill May 2022 -- December 2024
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Developed and maintained cross-platform mobile apps (Flutter, iOS, Android).
	\item Led key projects as project manager and technical owner, ensuring timely delivery.
	\item Integrated REST APIs, WebSockets, and real-time features (SignalR).
	\item Implemented offline-first solutions with local databases (Drift, SQLite, Isar).
	\item Enhanced app performance, stability, and error tracking with modern logging systems.
	\item Collaborated with product teams and clients to align business goals with technical execution.
\end{itemize}
\textbf{\href{https://www.terrabilgiisilem}{Terra Bilgi İşlem}. \textit{(Istanbul, Türkiye)}} \hfill Istanbul, Türkiye\\
\textit{Software Engineer} \hfill October 2011 -- May 2022
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Built and scaled educational platforms and mobile apps for iOS, Android, and desktop.
	\item Served as project lead for multiple large-scale educational apps (TEA ecosystem).
	\item Delivered solutions combining iOS/macOS apps with backend systems (JSP, Java, Node.js).
	\item Implemented secure, user-friendly apps for schools, universities, and corporate clients.
	\item Contributed to long-term projects, ensuring maintainability and scalability.
\end{itemize}
\section{Skills}
\textbf{Programming Languages:} Swift, SwiftUI, Objective-C, Java, Kotlin, Dart\\
\textbf{Backend Frameworks \& Runtimes:} Node.js, Express.js\\
\textbf{Frontend Frameworks \& Runtimes:} Flutter\\
\textbf{Databases:} MongoDB, MySQL\\
\textbf{Other:} Git, RestAPI, WebSocket, SignalR, Postman, Swagger
\section{Education}
\textbf{Eskisehir Anadolu University} \hfill Eskişehir, Türkiye\\
\textit{Bussines Administration} \hfill September 2013 -- June 2021\\
\textbf{Ankara University} \hfill Ankara, Türkiye\\
\textit{B.Sc. in Computer Engineering} \hfill September 2004 -- June 2009\\
\section{Scholarships}
\end{document}
